Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-13 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
Updating features extraction section

  \item[Earliest Starting Time (EST)] attribute represents the earliest possible execution time for an operation. It is calculated by accumulating the processing time of all preceding operations. This feature has a specific value $\mathit{Zero}$ if the operation has no predecessors.\todo{This value does not appear in the table, why?}

@@

  \item[Starting Time (ST)] is a set of features representing the starting execution time of each operation by solving the problem using a heuristic. In our work, we consider EST (\stest), First-In-First-Out (\stfifo), and Most Total Work Remaining (\stmtwr), see \cite{jones1998survey} for an overview.
  To compute the starting time, we use a simple greedy algorithm \cite{el2020job} that at each step selects a not scheduled operation according to the heuristics and schedules it to a machine. In the case of FIFO, the algorithm selects an operation that appeared first in the queue. Similarly, for MTWR, the algorithm selects the operation that belongs to the job with the longest processing time from the queue.

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used the same greedy algorithm as above with three different heuristics EST (\wtest), FIFO (\wtfifo), and MTWR (\wtmtwr). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and its earliest possible starting time. The latter is the maximum out of the end processing time of the operation's predecessor and the earliest time at which the required machine became available.

  \todo{It would be nice to add examples of other features to the table. If this is complicated, then only of \wtest and \stest.}
\end{description}

\begin{table}[h!]
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
  \caption{Features extracted for the sample problem instance.}
  \label{tab3}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c  c  c  c}
      \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML}\\
      \hline
										\\
      $O_{1,1}$  & 17 & 0   & 20	\\
      $O_{1,2}$  & 8  & 9   & 3		\\
      $O_{1,3}$  & 5  & 12 & 5		\\
										\\
      $O_{2,1}$  & 12 & 0   & 10	\\
      $O_{2,2}$  & 8  & 4   & 11	\\
      $O_{2,3}$  & 2  & 10 & 7		\\
					    					\\
      $O_{3,1}$  & 12 & 0  & 11	\\
      $O_{3,2}$  & 8  & 4  & 6		\\
      $O_{3,3}$  & 5  & 7  & 5		\\
    \end{tabular}
%\end{adjustwidth}

>>>>

  \item[Earliest Starting Time (EST)] attribute represents the earliest possible execution time for an operation. It is calculated by accumulating the processing time of all preceding operations. This feature has a specific value $0$ if the operation has no predecessors.%\todo{This value does not appear in the table, why?}

@@

  \item[Starting Time (ST)] is a set of features representing the starting execution time of each operation by solving the problem using a heuristic. In our work, we consider EST (\stest), First-In-First-Out (\stfifo), and Most Total Work Remaining (\stmtwr), see \cite{jones1998survey} for an overview.
  To compute the starting time, we use a simple greedy algorithm \cite{el2020job} that at each step selects a not scheduled operation according to the heuristics and schedules it to a machine. In the case of FIFO, the algorithm selects an operation that appeared first in the queue. For example, $O_{2,2}$ and $O_{3,3}$ are in the queue at time $9$ on machine $2$. Since $O_{2,2}$ and $O_{3,3}$ were ready to be processed at time $4$ and $7$, respectively. The algorithm selects $O_{2,2}$ to process at time $9$ before $O_{3,3}$ which starts at time $15$. Similarly, for MTWR, the algorithm selects the operation that belongs to the job with the longest processing time from the queue.

  \item[Waiting Time (WT)] is also a set of features, like ST, for which computation we used the same greedy algorithm as above with three different heuristics EST (\wtest), FIFO (\wtfifo), and MTWR (\wtmtwr). Each feature in \textit{WT} set is the difference between the scheduled starting time of a particular operation and ending time of its predecessor. %The latter is the maximum out of the end processing time of the operation's predecessor and the earliest time at which the required machine became available. 
  As shown in Table~\ref{tab3}, the predecessor of $O_{2,2}$ which is $O_{2,1}$ is finished at time $4$. However machine $2$ that executes $O_{2,2}$ was not free at that time, so $O_{2,2}$ had to wait $5$ time units to start the processing.

  %\todo{It would be nice to add examples of other features to the table. If this is complicated, then only of \wtest and \stest.}
\end{description}

\begin{table}[h!]
\setlength{\tabcolsep}{10.0pt}
\centering
  \begin{center}
  \caption{Features extracted for the sample problem instance.}
  \label{tab3}
 %\begin{adjustwidth}{0.0cm}{}
    \begin{tabular}{c  c  c  c  c  c}
      \textbf{Operation} & \textbf{RPT} & \textbf{EST} & \textbf{ML} & \textbf{\stfifo} & \textbf{\wtfifo}\\
      \hline
										\\
      $O_{1,1}$  & 17 & 0   & 20	&  0  & 0\\
      $O_{1,2}$  & 8  & 9   & 3		&  9  & 0\\
      $O_{1,3}$  & 5  & 12  & 5	  &  12 & 0\\
										\\
      $O_{2,1}$  & 12 & 0   & 10	&  0  & 0\\
      $O_{2,2}$  & 8  & 4   & 11	&  9  & 5\\
      $O_{2,3}$  & 2  & 10  & 7	  &  17 & 2\\
					    					\\
      $O_{3,1}$  & 12 & 0  & 11	  &  0  & 0\\
      $O_{3,2}$  & 8  & 4  & 6		&  4  & 0\\
      $O_{3,3}$  & 5  & 7  & 5		&  15 & 8\\
    \end{tabular}
%\end{adjustwidth}
